Meta-analysis of composite outcomes in clinical trials

### 2025-01-28 MSc_poster_template.Rmd
More feedback addressed

You can even use the bibliography the same way: Our data were taken from a cluster-randomised trial [^2], available from the [Irish Social Science Data Archive](https://www.ucd.ie/issda/data/).

[^2]: Murphy et al. 2005 doi: 10.1186/1468-6708-6-11

@@

The power of the permutation test is estimated using sampling with replacement. Participants are randomly resampled from the original data, allowing duplicates, while maintaining equal numbers from both treatment groups. The test is repeated multiple times, and power is determined by the proportion of resampled subsets yielding test statistics more extreme than the significance threshold.

@@

* Compare the permutation test method with the approach Mc Menamin *et al.*, [^5] used to analyze composite outputs.
* Compare different methods of creating the composite and their influence on power.
* Derive a theoretical distribution incorporating correlation between the variables.

>>>>

You can even use the bibliography the same way: Our data were taken from a cluster-randomised trial, available from the [Irish Social Science Data Archive](https://www.ucd.ie/issda/data/).

@@

The power of the permutation test is estimated using sampling with replacement. Participants are randomly resampled from the original data, allowing duplicates, while maintaining equal numbers from both treatment groups. The test is repeated multiple times, and power is determined by the proportion of resampled subsets yielding test statistics more extreme than the 5% significance threshold.

@@

* Compare the permutation test method with the approach Mc Menamin *et al.*, [^5] used to analyze composite outputs.
* Compare different methods of creating the composite test statistic and their influence on power.
* Derive a theoretical null distribution for the composite test statistic incorporating the correlation between the variables.
